% \documentclass[14pt, letterpaper]{article}
\documentclass[14pt, letterpaper]{extarticle}

\usepackage[letterpaper, inner=1.5in, outer=1.5in, top=1.5in, bottom=1.5in]{geometry}

\usepackage{fouriernc}

\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
% \usepackage{blindtext}

% make text look better
\usepackage{microtype}

% prevents hyphenation
\usepackage[none]{hyphenat} 

% use images
\usepackage{graphicx}

% wrap text around images
% \usepackage{wrapfig}

% make lists look better
% \usepackage{enumitem}

% fancy headers
% \usepackage{fancyhdr}

% math formulas
% \usepackage{amsmath}

% auto-generate indices
% usepackage{index}

% typography
% ragged right, left aligned
\usepackage[document]{ragged2e}
% control paragaph indents
\setlength{\parindent}{0em}
% line spacing
\renewcommand{\baselinestretch}{1.0}

% remove page numbering
\pagenumbering{gobble}

 \begin{document}
 \title{\LARGE{Very Far Away}}
 \author{\normalsize{Jimmy Ha}}
 \date{}
  
\maketitle

We flew on a plane, several planes. We are in an exciting new place. There are so many strange things to see and hear. Try the fried octopus! Take the 1:37 train.  If I don't take a picture of it, I might forget about it. I think our experience was unique. The other tourists we saw certainly didn't taste what we did. 

\vspace{1\baselineskip}
Here is my album of vacation snapshots. Some pictures have people who live and work in the places we visited. For them, it's just Tuesday.  

\vspace{1\baselineskip}
It feels lonely to be surrounded by so many unfamiliar things. The holiday didn't last long enough, but we miss home already. Let's do this again next year at newer and more exotic place. Somewhere where the trees and ferns are unlike the ones to which we're accustomed.

\vspace{1\baselineskip}
There are  buildings, flowers, tunnels that definitely belong from this vacation but not that other vacation. The memories of these places are as accurate as the colors in their pictures. I forgot the directions.




% \vspace{1\baselineskip}
% 13 December, 2021
  
  \end{document}
  