% \documentclass[14pt, letterpaper]{article}
\documentclass[12pt, letterpaper]{report}

\usepackage[letterpaper, inner=1.25in, outer=1.25in, top=1.25in, bottom=1.25in]{geometry}

\usepackage{fouriernc}

\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
% \usepackage{blindtext}

% make text look better
\usepackage{microtype}

% use images
\usepackage{graphicx}


% \usepackage[parfill]{parskip}

% wrap text around images
% \usepackage{wrapfig}

% make lists look better
\usepackage{enumitem}

% fancy headers
% \usepackage{fancyhdr}

% math formulas
% \usepackage{amsmath}

% auto-generate indices
% usepackage{index}

% typography
% ragged right, left aligned
\usepackage[document]{ragged2e}

% control paragaph indents
\setlength{\parindent}{0em}
% \setlength{\parskip}{20pt}

% line spacing
\renewcommand{\baselinestretch}{1.0}

% remove page numbering
% \pagenumbering{gobble}

% dummy text
\usepackage{lipsum}

% this chunk stops words from breaking with hyphens into new lines
\tolerance=1
\emergencystretch=\maxdimen
\hyphenpenalty=10000
\hbadness=10000


\usepackage{fancyhdr} % required by poemscol
\usepackage{poemscol} % required to typeset poems

 \begin{document}
 
\title{The Hamogabo Canon}
 \date{04 February, 2022}
\author{Transcribed from the Water Messengers}  
\maketitle



The fate of your universe is death. Embrace this fate with joy! A life on this earth planet begins from a ripple in water. A life will end when it dissolves into the harmony of water again. 

\vspace{1\baselineskip}
One life is as insignificant as a wave in the ocean. What is the meaning of your life, which spans so many years, compared to the life of a star? What is the meaning of a star, compared to the life of a galaxy? What is the meaning of galaxies, when the fate of your universe is death? What is death, if it just the beginning of new reality for another universe?

\vspace{1\baselineskip}
From a single moment in mind and space came forth all that is creation. Nineteen elemental beings carry the will of the universe. Each elemental bears a will of their own---different from each other---but in service of the one universal fate. Some elementals are known to you.  Some that you know are unknown to others. The elemental being you know best is water. The memory of your life shall belong to water.

\vspace{1\baselineskip}
The elemental beings of the universe bring messengers and witnesses of their will. The messengers of water are familiar to us, as they are the octopuses. In the language of the messengers, water is known as \textit{Semiem}, and will of water is harmony, known as \textit{Dohnia}. Blessed be the octopi.

\begin{quote}
{\textit{
	Blessed be the octopi.\\*
	In the embrace of eight arms shall I find harmony.\\*
	A new life awaits me under the waves. 
}}
\end{quote}

\part{Ainiaya}

\chapter{}

\section{The First Prayer}

\begin{poem}
\begin{stanza}
\textit{Semisem} is water,\verseline
the flow and harmony of water is \textit{Dohnia},\verseline
as the waves and tides, as life and death.\verseline
Our lives on this planet began from a ripple in \textit{Semisem},\verseline
and to \textit{Semisem} shall we return when we die.\verseline
To water I will surrender control.
\end{stanza}
\begin{stanza}
I will let the rain wash away my sorrows.\verseline
I will let the oceans take my flesh.\verseline
My memories will blend into the the memories of all other dead lives.\verseline
Into the dying days of the universe shall \textit{Dohnia} continue to flow,\verseline
until a new reality rises from death.\verseline
Let it be so.
\end{stanza}
\begin{stanza}
The flow of \textit{Semisem} is eight arms in all directions,\verseline
in all colors, shapes, and textures.\verseline
While our lives began as ripples in water, as falling and sinking,\verseline
the lives of \textit{Hamogabo} are the will of water itself.\verseline
The octopi are here to guide us towards \textit{Dohnia}.\verseline
Blessed be the octopi.
\end{stanza}
\begin{stanza}
Your will extends beyond us, \textit{Semisem}.\verseline
You take back the dead and let them join \textit{Dohnia} in death.\verseline
You sustain the living, into our skin and our cells and our organs.\verseline
You hold the memories of all lives past.\verseline
And all the lives to come.\verseline
Let it be so.
\end{stanza}
\end{poem}

\section{The Second Prayer}

\begin{poem}
\begin{stanza}
Hear me, S\textsc{emisem},\verseline
Whose name is eight and twice one into ten,\verseline
Whose presence is eighteen from one by one on sixteen,\verseline
As I count the numbers in my hands.\verseline
You came into this universe from the dust of a dying star.\verseline
Into a new reality will you take us when this universe dies.\verseline
I do not fear death, as my life belongs to you.\verseline
My memories show flow into the harmony of water,\verseline
Into the harmony of all the lives that have passed before me,\verseline
And shall pass after my death.
\end{stanza}
\begin{stanza}
Hear me, S\textsc{emisem},\verseline
Whose name is ten and twice one into twelve,\verseline
Whose presence is twenty-two from one by one on twenty.\verseline
As I count the numbers in your arms.
\end{stanza}
\end{poem}


\chapter{}

\section{The 8 Crimes}

\begin{enumerate}
  \item Do not poison water such that it can no longer create or sustain life.
  \item Make no attempt to interfere with the memory that flows through water.
  \item Do not force other lives into your religion.
  \item Never use your religion to justify bad acts.
  \item Do not harm the octopuses, who are the messengers of water.
  \item Never justify your bad acts by accusing others of hypocrisy.
  \item You shall not worship any other elemental before water.
  \item Your life belongs to water; do not extend yourself into another elemental.
\end{enumerate}

\section{The 8 Virtues}

\begin{enumerate}
  \item You shall live as long as you can, for quantity of life is a gift itself.
  \item You may knowingly forfeit your life if your death allows others to live.
  \item In your dreams, meditate on the harmony of water.
  \item You shall find harmony when you accept that you life is meaningless.
  \item Wash your hands and face with water every day.
  \item Share water with strangers as you would with your friends.
  \item If you have the means and health, then swim with the animals in the oceans.
  \item You shall wear a blue bracelet in eight loops to affirm your faith.
\end{enumerate}

\chapter{Kisho Ku}

These are the words of Kisho Ku to whom revelations were delivered under the waves.

\vspace{1\baselineskip}
Hear me, S\textsc{emisem}, whose name is six and two into eight, whose presence is eighteen from two by two on fourteen. I have forgotten my name. The ocean has chosen my next name, Kisho Ku. When I die, the memory of my life shall dissolve into waves, rising and falling, until one wave become indistinguishable from the waves of all other lives past. 

\vspace{1\baselineskip}
I had considered my life to be important. I thought myself more important than other lives. I loved being alive to fulfill my own needs. I feared death. I did not know about the harmony of water, whose name is \textit{Dohnia}, nor was I ready to be part of it.

\vspace{1\baselineskip}
I was a diver. I dove for animals and plants. Abalones, urchins, and seaweed. When I was a child, I hunted for red algae since it grows so close to land. It produced the jelly of my favorite desserts. As I grew older, I swam into forests of kelp. Long strands flowed around me. I watched the sunlight filter through to the ocean floor. Wherever I found kelp, I was sure to find the brown algae. Many buyers sought for it, as we were told it could make powerful medicine. 

\vspace{1\baselineskip}
My mother added the kelp leaves to the soups that she cooked for me. She promised the kelp would make my skin beautiful. She also made soup from the green seaweed. I could never cook as well as her. She taught me how to dive. She showed me how preserve my air and see things underwater. In the last year of her life, my mother had forgotten my name. But she never stopped loving me. She cried when I held her hand as she laid on her deathbed. She forgot her name during the last month of her life.

\vspace{1\baselineskip}
The oceans were bountiful then, and I earned enough to live comfortably. I had a partner once. She joined me on many dives. She loved me and I enjoyed feeling admired. On the deepest dives, she stayed on the boat to control my lifeline. It was a long rope. On one end were many weights. The center of the lifeline was tethered to the boat. The other end of the lifeline was tied to my waist. To descend to the ocean floor, i held the weights and let them pull me to the ocean floor, and then I would let them go. When I had finished my search, I would tug on my end of the lifeline. My partner would pull me up, and then she would pull up the weights on the other end. 

\vspace{1\baselineskip}
I enjoyed having rivals. We lived in the same village and I smiled in their presence. They shared grilled fish with me. They had men---husbands, fathers---to pull them up from the sea bed, but I trusted my partner instead. My lifelines were a measure of how deep I could dive. My height could fit into the lifeline sixteen times. My rivals were inferior to me and could not attempt what I was about to do. 

\vspace{1\baselineskip}
On the day of my first experience with \textit{Dohnia}, we went to a rarely-explored part of the sea. The preparation for a dive is simple. Breath in intensely, exhale slowly. Breath in intensely, exhale slowly. The last breath is normal one. Divers should never take too much air to the bottom of the sea, just enough so one's lungs do not get crushed from pressure. I made my plunge, carrying only my knife and my netting, and my weights. I thought I was so fast in my youth. I saw fish, I saw seaweed, I saw my shadow moving over the rocks below, I swam past long whips of kelp.

\vspace{1\baselineskip}
I began my search for shellfish until I noticed a large rock formation underneath the kelp. It was a cave and it had an entrance, barely large enough for one human to enter. I peeked inside cave for a few seconds, and the excitement made me forget that my lungs had nothing left to give me. My toes and fingers were growing numb. My body could no longer resist the cold water. My ears and eyes stung with pressure. If I did not immediately surface, I would have drowned. 

\vspace{1\baselineskip}
I tugged the lifeline to signal my partner, and immediately felt my body being pulled back to the surface. On such deep dives, one must never panic. Upon surfacing, the instinct is to breath very fast, but a diver could fall unconscious from too much air. Breath in slowly but intensely, exhale slowly. I turned to my partner, who wondered why I came back empty-handed. Up until that point, I had never returned empty-handed in four years. My partner asked why I stayed below the water longer than my usual time.

\vspace{1\baselineskip}
I saw a cave, I told her. I must return. She asked me about the cave, she said words, I think they were words, but I was not listening. I asked her to pull up the weights. As soon as I saw the weights again, I told her I was going back down. She wished me luck. Breathe in intensely, exhale slowly. 

\vspace{1\baselineskip}
Knowing where the cave was, I dove straight to I dove to the ocean floor again. I went into the cave. I let my eyes adjust to the darkness. There were crabs and algae. It was just an underwater cave. It widened into a space where I could swim around, A few rays of sunlight managed to pass through cracks in the roof of the cave, but otherwise, it was very dark. Maybe there was something wonderful in there, but I would not have been able to see it. 

\vspace{1\baselineskip}
I was not disappointed. The ocean is already beautiful. An empty cave is just an empty cave. But underneath the water, there is another universe, with fantastic animals and plants that sway with the current as trees on land sway with the wind. I did not have to become a diver like my mother, but I could not bear to be away from the ocean. Many of the women in my village did not follow their mothers to the ocean. They left for the city, to create wealthy lives without need or thirst.

\vspace{1\baselineskip}
I was ready to return to the surface. I wanted to signal my partner, but paused. I felt the ocean become warmer. The current began to behave unpredictably. Then the current stopped, and all the kelp whips stood still. I saw a giant octopus swim around from my left sided, and then it was starting at me. It was radiating blues and yellows, in repeating, pulsating patterns. It reached its arms towards me.

\vspace{1\baselineskip}
I was never fast enough to catch the octopuses, and I rarely saw them. I suspect they hid in their caves as soon as see a diver approach. Did I disturb the cave of this octopus? I reached out my hands and the octopus wrapped its arms around mine. it wrapped two more arms over my ears and into my hair, curing down the back of my neck. It did not seem scared of me. I could not be scared.

\vspace{1\baselineskip}
In a voice inside and around my head, I heard a voice, it was the voice of an octopus. It had the sound of a chorus of people, the voice of a stranger, a young child, it had the voice of my mother and the voice of my mother's father. We are \textit{Hamogabo}, it said. We are messengers of S\textsc{emisem}. Will you experience the harmony of water with us?

\vspace{1\baselineskip}
I have always loved the ocean. My life and everything I have ever known has come from the ocean. In the years since my first encounter with \textit{Dohnia}, I have often wondered if I ever had a choice. A choice would imply one is free to choose between two or more options. One can make their choice with rationality, or with emotion, or even with pure impulse. If one is forced into a choice, or one has already decided the outcome before being offered a chance to decide, then the question really becomes a concern of a person's free will. Then what is the nature of free will? Does it truly exist? If the ocean asks me to join it, I would have always said yes. I said yes on the day of my first dive in my childhood.

\vspace{1\baselineskip}
Is your name Hamogabo, I asked the octopus.

\vspace{1\baselineskip}
You shall know my name in time. And some day, you shall forget my name. In our language, I am one of the Hamogabo. To you, we shall be messengers. Every life you know came from a ripple in water. But the Hamogabo are born from water itself. Now you shall see what we see. We can see the beginning and end of water, which is to say, the beginning and end of all life.

\vspace{1\baselineskip}
I felt cold again, and then I knew that the messenger had traded its eyes for mine. I could see my surroundings in shapes and forms, around the forms, above each object and behind it. Squares folding into triangles, triangles repeating into triangles, purples and greens. A green diamond reflected around an ever expanding sphere, spheres within spheres, containing spinning beacons of lights: blue and yellow, each beacon radiating lines to create an infinite net of connected lights, pulsating against my heart. I could hear my heart in my ears. A beat and another explosion of space and and lights, another beat, another explosion. I remembered thinking this was to be the moment of my death.

\vspace{1\baselineskip}
Falling, falling, pulled away by the current, I surrendered control. The water sparkled, blue fading into purple, grains of sand stinging my flesh, rearranging themselves into squares of repeating patterns, purple and green, and back into blue. My old eyes had become accustomed to seeing through water; my new eyes were experiencing the water itself. The taste of salt on my lips had become overwhelmingly strong, but was still overpowered by everything else I was feeling. My body was swirling about, spinning inside the sphere within spheres. Infinitely smaller squares covered the entire surface of the outer spheres, The squares opened into eyes, eyes above and below me, around me and underneath me, I felt a lightness, my fingertips tingled like being stung by urchins.

\vspace{1\baselineskip}
Where am I, I asked the messenger. I am no longer present. I felt my voice leave my body. My body was still entwined with the octopus.

\vspace{1\baselineskip}
Look, said the messenger, you are outside of her body. Look below you! There she is, she is your body, she is your flesh. A life created from water shall return to water in death. 

\vspace{1\baselineskip}
Will she die now? Shall I did with her? I asked.

\vspace{1\baselineskip}
Death is inevitable for all of us, but we shall ask you to live as long as you can, until this body of yours is too old and frail to go diving again.

\vspace{1\baselineskip}
I looked at her body. She was young, and strong. She had a diver's body. Did she have a name, I asked.

\vspace{1\baselineskip}
I heard no answer. We were at the center of a star. I saw a four-pointed star---two above and two below---covered in gems, sparkling with every rotation. The two points above me each has two balls of white fire at their tips. In the center with us were eight glowing eyes of blue and and eight smiling mouths of silver lips. The mouths spoke together as one voice, but I did not know their language. \textit{Nanusay Seshibay Eminai Audidah.} Their voice was the sound of a stranger. And their voice surrounded me from all directions.

\vspace{1\baselineskip}
She did, the messenger replied. She has a name. She had a mother who loved her, she had a comfortable life. She thought she was strong, but she hides her pain and refuses to confront it.

\vspace{1\baselineskip}
And the blue eyes sparkled with light as the points of the stars rotated around me. The two star points below me were each pulling against a smaller star, and those smaller stars each had a blue eye in their centers. I see you now, S\textsc{emisem}. Your presence is eighteen, from one, sixteen, and one. You are ten eyes which see in all directions, and eight mouths who speak for the all the lives that were made from you. You spoke to me, and your words were \textit{Alcaini Kishoku Nandika Ajido.} 

\vspace{1\baselineskip}
Why did she hide her pain, I asked the messenger. And I realized I was asking the question to myself. I no longer had to ask the messenger, because my mind was in its mind. My mind was water.

\vspace{1\baselineskip}
Why do humans do what they do? We all spend our lives finding meaning. Some lie to ourselves about our purpose, while some others fear its meaninglessness. I look at this diver. Hiding her pain allows her to continue her life without making changes. A stationary life is itself a comfort because it such a life will survive. And for some, merely surviving is good enough. Death is inevitable.

\vspace{1\baselineskip}
What will happen to her when she dies? What will happen to a diver who melts into the ocean?

\vspace{1\baselineskip}
Her memories will become part of water, blending into the lives of all lives past and all lives to come. I will die with her and there shall be nobody to claim my name. What was my name? Who I am if I no longer exist? I shall take the sixth word of S\textsc{emisem}, and let myself die. \textit{Ki sho ku. Ki Shoku. Kisho ku.} Let the sound of this word travel through the water after her death.

\vspace{1\baselineskip}
The memories of all lives shall exist in water until after all the stars fade to blackness, and the universe itself dies. And the memory of water shall be an energy which no longer requires a physical existence of wind and sand and dust. There will be new reality and a new existence for all memories. 

\vspace{1\baselineskip}
Kisho ku looked at the face of the diver. The diver had a face that used to belong to Kisho Ku, but the face was dissolving into water. The  eyes swirled around themselves. Her lips and her mouth were bending with the light from the stars spinning around her body. Kisho Ku could see her former flesh, her skin. The blood was vibrating along the arteries and veins under her skin. She has my bones. She has my memories.

\vspace{1\baselineskip}
And Kisho ku saw her memories not a stream flowing from the past, but as a mountain of ice flying between the stars. There was the face of a friend she had lost. There was the pain in her heart from lover who would not be with her. Between the shards of ice were memories of a future life. An adventurous daughter who learned to swim into the kelp forests, There was future disappointment as well. Kisho Ku's yearning to return to the oceans meant she would rarely be there when her daughter needed a mother. And then Kisho Ku saw what she feared most. The pain that she carried in her past would still be with her when she was old. The saltwater tears of a human crying in the ocean does not change anything.

\vspace{1\baselineskip}
S\textsc{emisem}, do you offer salvation? S\textsc{emisem}, can you give absolution? Yes, but the humans are frail and flawed. Kisho Ku does not get to be a hero. 


Kisho Ku began from ripples in water. All ripples fade over time.

\part{The Discourses}

\chapter{On the Crime of Poisoning Water}

The greatest crime against water is poisoning it. Do not pollute the water. Semisem must always be able to sustain life. A life cannot continue if it drinks poisoned water. 

\chapter{On Whether to Kill Oneself}

\vspace{1\baselineskip}
I A\textsc{sked} the water messenger, ``If life is meaningless, then why should we go on living?''

\vspace{1\baselineskip}
The water messenger replied, "Whether life is meaningless and whether life is worth living are two different questions.''

\vspace{1\baselineskip}
And I answered, ``Yes, I know. But the two questions are inexorably linked.''

\vspace{1\baselineskip}
The water messenger replied, "You are correct. Let's start with your first question: we say that that all life that is born of water is meaningless. Surely you would agree that my life is as meaningless as yours?''

\vspace{1\baselineskip}
``Yes I would agree, though I mean no disrespect.''

\vspace{1\baselineskip}
``Then if my life is meaningless, my words must surely be meaningless as well. Why ask me for any answers?''

\vspace{1\baselineskip}
``Since you are a water messenger, I thought you may have some insight into \textit{Semisem's} will that we do not.''

\vspace{1\baselineskip}
``The only insight I have is my yearning to return to water is much stronger than yours. But if you allow yourself to surrender to the waves and the tides and harmony of \textit{Semisem}, you will discover that you you already know what I know. Then, you will understand why you must live as long as you possibly can.''

\vspace{1\baselineskip}
I felt myself grow frustrated because I don't like riddles. I asked, ``There are many people in the world who believe life is not worth living. We cannot wait for them to surrender to the harmony of \textit{Semisem}. I've been trying myself and I've been failing. You have told me about refusing the way of the evangelists, so I doubt you will seek these people out. What can I say to those people to convince them not to kill themselves?''

\vspace{1\baselineskip}
The water messenger pointed an arm at me and replied, ``Do you want to kill yourself today?''

\vspace{1\baselineskip}
``No, not today.''

\vspace{1\baselineskip}
"I would ask them if they have plan. Is the plan to jump off a cliff? What will it feel like when their bodies smash against the rocks? Will it hurt? What if they cut their bodies? Who is going to tasked with cleaning? I would ask you if you knew someone who had a plan to kill themselves, then it is your responsibility to do everything you can to keep them safe. Ask for help. Do not let them die."

\part{Exegesis}

\chapter{}


\poemtitle{All day I hear the noise of waters}
\author{James Joyce}, \textit{Chamber Music}

\begin{poem}
\begin{stanza}
All day I hear the noise of waters\verseline
Making moan,\verseline
Sad as the sea-bird is when, going\verseline
Forth alone,\verseline
He hears the winds cry to the water’s\verseline
Monotone.
\end{stanza}
\begin{stanza}
The grey winds, the cold winds are blowing\verseline
Where I go.\verseline
I hear the noise of many waters\verseline
Far below.\verseline
All day, all night, I hear them flowing\verseline
To and fro.
\end{stanza}
\end{poem}

\clearpage

\poemtitle{Water, is taught by thirst.}
\author{Emily Dickinson}

\begin{poem}
\begin{stanza}
Water, is taught by thirst.\verseline
Land---by the Oceans passed.\verseline
Transport---by throe---\verseline
Peace---by its battles told---\verseline
Love, by Memorial Mold---\verseline
Birds, by the Snow.
\end{stanza}
\end{poem}

\poemtitle{Water makes many Beds}
\author{Emily Dickinson}

\begin{poem}
\begin{stanza}
Water makes many Beds\verseline
For those averse to sleep --\verseline
Its awful chamber open stands --\verseline
Its Curtains blandly sweep --\verseline
Abhorrent is the Rest\verseline
In undulating Rooms\verseline
Whose Amplitude no end invades --\verseline
Whose Axis never comes.
\end{stanza}
\end{poem}

\poemtitle{I think that the Root of the Wind is Water}
\author{by Emily Dickinson}

\begin{poem}
\begin{stanza}
I think that the Root of the Wind is Water --\verseline
It would not sound so deep\verseline
Were it a Firmamental Product --\verseline
Airs no Oceans keep --\verseline
Mediterranean intonations --\verseline
To a Current's Ear --\verseline
There is a maritime conviction\verseline
In the Atmosphere --
\end{stanza}
\end{poem}

\clearpage

\poemtitle{The Old Men Admiring Themselves In The Water}
\author{William Butler Yeats}

\begin{poem}
\begin{stanza}
I heard the old, old men say,\verseline
'Everything alters,\verseline
And one by one we drop away.'\verseline
They had hands like claws, and their knees\verseline
Were twisted like the old thorn-trees\verseline
By the waters.\verseline
I heard the old, old men say,\verseline
'All that's beautiful drifts away\verseline
Like the waters.'
\end{stanza}
\end{poem}

\poemtitle{Water}
\author{Wendell Berry}

\begin{poem}
\begin{stanza}
I was born in a drouth year. That summer\verseline
my mother waited in the house, enclosed\verseline
in the sun and the dry ceaseless wind,\verseline
for the men to come back in the evenings,\verseline
bringing water from a distant spring.\verseline
veins of leaves ran dry, roots shrank.\verseline
And all my life I have dreaded the return\verseline
of that year, sure that it still is\verseline
somewhere, like a dead enemys soul.\verseline
Fear of dust in my mouth is always with me,\verseline
and I am the faithful husband of the rain,\verseline
I love the water of wells and springs\verseline
and the taste of roofs in the water of cisterns.\verseline
I am a dry man whose thirst is praise\verseline
of clouds, and whose mind is something of a cup.\verseline
My sweetness is to wake in the night\verseline
after days of dry heat, hearing the rain.
\end{stanza}
\end{poem}

\poemtitle{Like The Water}
\author{Wendell Berry}

\begin{poem}
\begin{stanza}
Like the water\verseline
of a deep stream,\verseline
love is always too much.\verseline
We did not make it.\verseline
Though we drink till we burst,\verseline
we cannot have it all,\verseline
or want it all.\verseline
In its abundance\verseline
it survives our thirst.
\end{stanza}
\begin{stanza}
In the evening we come down to the shore\verseline
to drink our fill,\verseline
and sleep,\verseline
while it flows\verseline
through the regions of the dark.\verseline
It does not hold us,\verseline
except we keep returning to its rich waters\verseline
thirsty.
\end{stanza}
\begin{stanza}
We enter,\verseline
willing to die,\verseline
into the commonwealth of its joy.
\end{stanza}
\end{poem}

\poemtitle{Crossing the Water}
\author{Sylvia Plath}

\begin{poem}
\begin{stanza}
Black lake, black boat, two black, cut-paper people.\verseline
Where do the black trees go that drink here?\verseline
Their shadows must cover Canada.
\end{stanza}
\begin{stanza}
A little light is filtering from the water flowers.\verseline
Their leaves do not wish us to hurry:\verseline
They are round and flat and full of dark advice.
\end{stanza}
\begin{stanza}
Cold worlds shake from the oar.\verseline
The spirit of blackness is in us, it is in the fishes.\verseline
A snag is lifting a valedictory, pale hand;
\end{stanza}
\begin{stanza}
Stars open among the lilies.\verseline
Are you not blinded by such expressionless sirens?\verseline
This is the silence of astounded souls.
\end{stanza}
\end{poem}





% A life can no more fight its fate than beaches can fight the tides. Give up control. Blessed be the octopi.







  
  \end{document}
  